---
title: "Bootstrapping"
author: "Te-Hsuan Huang"
date: "2025-11-28"
output: github_document
---

```{r}
library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

# make a series number
```{r}
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const |> 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)
```

# fit a model
```{r}
sim_df_const |> 
lm(y ~ x, data = _) |> 
  broom::tidy() |> 
  knitr::kable(digits = 3)

sim_df_nonconst |> 
lm(y ~ x, data = _) |> 
  broom::tidy() |> 
  knitr::kable(digits = 3)
```

# write a function for boostrap
```{r}
boot_sample = function(df) {
  sample_frac(df, size = 1, replace = TRUE)
}
```

* replace=TRUE: This is the crucial part. It means that after a row is selected, it is "replaced" back into the pool of rows and can be selected again.

* Test the function
```{r}
sim_df_nonconst |> 
boot_sample() |> 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm", se=FALSE)
```

# Draw many boostrap sample
```{r}
boot_straps = 
  tibble(strap_number = 1:5000) |> 
  mutate(
    strap_sample = map(strap_number, \(i) boot_sample(df = sim_df_nonconst))
  )

boot_straps
```

# Analyzing bootstrap samples
```{r}
bootstrap_results = 
  boot_straps |> 
  mutate(
    models = map(strap_sample, \(df) lm(y ~ x, data = df) ),
    results = map(models, broom::tidy)) |> 
  select(-strap_sample, -models) |> 
  unnest(results) 
```

* Summary
```{r}
bootstrap_results |> 
  group_by(term) |> 
  summarize(
    boot_estimate = mean(estimate),
    boot_se = sd(estimate)
    ) |> 
  knitr::kable(digits = 3)
```

* Look on the plot
```{r}
bootstrap_results |> 
  filter(term == "x") |> 
  ggplot(aes(x=estimate))+ 
  geom_density()
```

* Add CI
```{r}
bootstrap_results |> 
  group_by(term) |> 
  summarize(
    ci_lower = quantile(estimate, 0.025), 
    ci_upper = quantile(estimate, 0.975))
```

# do it faster
```{r}
sim_df_nonconst |> 
  modelr::bootstrap(n = 1000) |> 
  mutate(
    models = map(strap, \(df) lm(y ~ x, data = df) ),
    results = map(models, broom::tidy)) |> 
  select(-strap, -models) |> 
  unnest(results) |> 
  group_by(term) |> 
  summarize(
    boot_estimate = mean(estimate),
    boot_se = sd(estimate)
    )
```

* constant
```{r}
sim_df_const |> 
  modelr::bootstrap(n = 1000) |> 
  mutate(
    models = map(strap, \(df) lm(y ~ x, data = df) ),
    results = map(models, broom::tidy)) |> 
  select(-strap, -models) |> 
  unnest(results) |> 
  group_by(term) |> 
  summarize(
    boot_estimate = mean(estimate),
    boot_se = sd(estimate)
    )
```

# Change the dataset
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) |> 
  filter(borough != "Staten Island") |> 
  drop_na(price, stars, room_type) |> 
  select(price, stars, borough, room_type)
```

* make a plot
```{r}
nyc_airbnb |> 
  ggplot(aes(x = stars, y = price, color = room_type)) + 
  geom_point() 
```

* try to do bootstrap
```{r}
nyc_airbnb |> 
  filter(borough == "Manhattan") |> 
  modelr::bootstrap(n = 1000) |> 
  mutate(
    models = map(strap, \(df) lm(price ~ stars + room_type, data = df)),
    results = map(models, broom::tidy)) |> 
  select(.id, results) |> 
  unnest(results) |> 
  filter(term == "stars") |> 
  ggplot(aes(x = estimate)) + 
  geom_density()
```

* modelr::bootstrap(n = 1000): This tells R to generate 1,000 distinct bootstrap samples from the Manhattan-only data frame.
