---
title: "cross"
author: "Te-Hsuan Huang"
date: "2025-11-26"
output: github_document
---

# Load the package
```{r}
library(tidyverse)
library(modelr)
library(mgcv)
library(p8105.datasets)

set.seed(1)
```

# upload the data
```{r}
data("lidar")

lidar_df = 
  lidar |> 
  as_tibble() |>
  mutate(id = row_number())

lidar_df |> 
  ggplot(aes(x = range, y = logratio)) + 
  geom_point()
```

# Cross validation by hand
```{r}
train_df = sample_frac(lidar_df, size = .8)
test_df = anti_join(lidar_df, train_df, by = "id")

ggplot(train_df, aes(x = range, y = logratio)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```

# Using 3 model
```{r}
linear_mod = lm(logratio ~ range, data = train_df)
smooth_mod = mgcv::gam(logratio ~ s(range), data = train_df)
wiggly_mod = mgcv::gam(logratio ~ s(range, k = 30), sp = 10e-6, data = train_df)
```
* k=30, you are telling the model: "Use a maximum of 30 basis functions to model the relationship between range and logratio. This allows for a potentially much wigglier (more flexible) curve than the default setting."

# Add what i run in the model
```{r}
train_df |> 
  add_predictions(smooth_mod) |> 
  ggplot(aes(x = range, y = logratio)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red")
```

* Add more line on it
```{r}
train_df |> 
  gather_predictions(linear_mod, smooth_mod, wiggly_mod) |> 
  mutate(model = fct_inorder(model)) |> 
  ggplot(aes(x = range, y = logratio)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red") + 
  facet_wrap(~model)
```

# Looking at prediction accuracy
```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```
* Root Mean Squared Error: It answers the question: "On average, how far are my model's predictions from the actual observed values?"

# Using modelr package
```{r}
cv_df = 
  crossv_mc(lidar_df, 100) 
```

* See how the data look like
```{r}
cv_df |> 
  pull(train) |> 
  nth(1) |> 
  as_tibble()

cv_df |> pull(test) |> nth(1) |> as_tibble()
```

* Change every dataset as small table
```{r}
cv_df =
  cv_df |> 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

* Fit the model
```{r}
cv_df = 
  cv_df |> 
  mutate(
    linear_mod  = map(train, \(df) lm(logratio ~ range, data = df)),
    smooth_mod  = map(train, \(df) gam(logratio ~ s(range), data = df)),
    wiggly_mod  = map(train, \(df) gam(logratio ~ s(range, k = 30), sp = 10e-6, data = df))) |> 
  mutate(
    rmse_linear = map2_dbl(linear_mod, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_smooth = map2_dbl(smooth_mod, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_wiggly = map2_dbl(wiggly_mod, test, \(mod, df) rmse(model = mod, data = df)))
```

* map2_dbl: to iterate over two lists simultaneously and apply a function to pairs of elements, returning a numeric vector.

# Make the result easily to see
```{r}
cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") |> 
  mutate(model = fct_inorder(model)) |> 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

